[dcpo_demsupport]

### 2020-09-03 paper/dcpo_demsupport.Rmd
trimmed data updating

```{r claassenAJPS}
# Data input ----

supdem <- read.csv("../data/Support_democracy_ajps.csv")
v_dem <- read.csv("../data/vdem15.csv")

sd.plm <- pdata.frame(supdem, index = c("Country", "Year"))

# Pooled model -----

@@

```{r dcpoPointAJPS}
load(here::here("data", "dcpo_input.rda"))
load(here::here("data", "dcpo_theta.rda"))
load(here::here("data", "dcpo_sigma.rda"))

@@

@@

```{r claassenAPSR}
load("../data/dem_mood_apsr.RData")
sd.plm <- pdata.frame(x, index = c("Country", "Year"))

>>>>

```{r dataInput, eval = FALSE}

supdem <- read.csv("../data/Support_democracy_ajps.csv")
v_dem <- read.csv("../data/vdem15.csv")
sd.plm <- pdata.frame(supdem, index = c("Country", "Year"))

load(here::here("data", "claassen_m5_theta.rda"))
load(here::here("data", "dcpo_input.rda"))
load(here::here("data", "dcpo_theta.rda"))
load(here::here("data", "dcpo_sigma.rda"))
load(here::here("data", "dem_mood_apsr.RData"))

```

```{r claassenAJPS}
# Pooled model -----

@@

```{r claassenUncertainty}

@@

df_claassen <- purrr::map(1:1000, function(anEntry) {
  claassen_m5_theta$theta[anEntry,,] %>% 
    reformat_dcpo_output("theta") %>% 
    left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
              by = c("year", "country")) %>%
    left_join(df_controls, by = c("country", "year")) %>% 
    mutate(theta_dem = theta * regime,
           theta_aut = theta * (1 - regime)) %>% 
    plm::pdata.frame(index = c("country", "year"))
})

```{r dcpoPointAJPS}
ls_country <- levels(dcpo_input$data$kk)
first_year <- min(dcpo_input$data$year)

@@

```{r claassenAPSR}
sd.plm <- pdata.frame(x, index = c("Country", "Year"))
